---
title: "Project 2"
author: "Shelnes Elie"
date: "10/13/2020"
output:
  github_document: default
  rmarkdown::github_document: default
params:
  hub: weekday_is_tuesday
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Packages Required
library(tidyverse)
library(caret)

# install.packages("arsenal")
library(arsenal)

# install.packages("treefit")
library(treefit)

library(tree)
library(purrr)
library(knitr)
library(rmarkdown)



```



```{r readin data, echo = FALSE}

# Reading in the data utilizing relative path and current working directory
news0 <- as_tibble(read.csv("OnlineNewsPopularity.csv"))
# str(news)
# attributes(news)

# Filter data by day
if (params$hub == "weekday_is_monday"){
news1 <- filter(news0, weekday_is_monday == 1) %>%
  select(-url)} else if (params$hub == "weekday_is_tuesday"){
news1 <- filter(news0, weekday_is_tuesday == 1) %>%
  select(-url)} else if (params$hub == "weekday_is_wednesday"){
news1 <- filter(news0, weekday_is_wednesday == 1) %>%
  select(-url)} else if (params$hub == "weekday_is_thursday"){
news1 <- filter(news0, weekday_is_thursday == 1) %>%
  select(-url)} else if (params$hub == "weekday_is_friday"){
news1 <- filter(news0, weekday_is_friday == 1) %>%
  select(-url)} else if (params$hub == "weekday_is_saturday"){
news1 <- filter(news0, weekday_is_saturday == 1) %>%
  select(-url)} else if (params$hub == "weekday_is_sunday"){
news1 <- filter(news0, weekday_is_sunday == 1) %>%
  select(-url)}

# Sample and create train/test data
set.seed(1)
train <- sample(1:nrow(news1), size = nrow(news1)*0.7)
test <- dplyr::setdiff(1:nrow(news1), train)
newsDataTrain <- news1[train, ]
newsDataTest <- news1[test, ]

```

# _Introduction_

The data in this project represents the online news popularity. This dataset summarizes a heterogeneous set of features about articles published by Mashable in a period of two years. The goal is to predict the number of shares in social networks (popularity).Some of the variables used are:  
  
  + weekday_is/is_weekend = represents what day of the week or is it the weekend.  
  + shares = # of shares/target  
  + LDA = Close to LDA topic  
  + n_tokens_content = Number of words in the content  
  + data_channel_is_lifestyle = Is data channel 'Lifestyle'?  
  + data_channel_is_entertainment = Is data channel 'Entertainment'?  
  + data_channel_is_bus = Is data channel 'Business'?  
  + data_channel_is_socmed = Is data channel 'Social Media'?  
  + data_channel_is_tech = Is data channel 'Tech'?  
  + data_channel_is_world = Is data channel 'World'?  

# _Summarization_

The below summary describes the measure of center for shares.

```{r summarization, echo = FALSE}

# Summary Statistics
params$hub

summary(news1$shares)

```



```{r graphs_setup, echo = FALSE}
# Plots / Preparing Data

#Data channel is lifestyle
lifestyle <- filter(newsDataTrain,  data_channel_is_lifestyle == 1) %>%
  select( data_channel_is_lifestyle, shares,  n_tokens_content)

    lifestyle$data_channel_is_lifestyle <- case_when(
      lifestyle$data_channel_is_lifestyle==1 ~ "Lifestyle")

lifestyle <-rename(lifestyle, data_channel = data_channel_is_lifestyle)


#Data channel is entertainment
entertainment <- filter(newsDataTrain,  data_channel_is_entertainment == 1) %>%
  select( data_channel_is_entertainment, shares,  n_tokens_content)

    entertainment$data_channel_is_entertainment <- case_when(
      entertainment$data_channel_is_entertainment==1 ~ "Entertainment")

entertainment <-rename(entertainment, data_channel = data_channel_is_entertainment)


#Data channel is bus
bus <- filter(newsDataTrain,  data_channel_is_bus == 1) %>%
  select( data_channel_is_bus, shares,  n_tokens_content)

    bus$data_channel_is_bus <- case_when(
      bus$data_channel_is_bus==1 ~ "Bus")

bus <-rename(bus, data_channel = data_channel_is_bus) %>%
  filter(shares < 3000) # Eliminate outlier


#Data channel is socmed
socmed <- filter(newsDataTrain,  data_channel_is_socmed == 1) %>%
  select( data_channel_is_socmed, shares,  n_tokens_content)

    socmed$data_channel_is_socmed <- case_when(
      socmed$data_channel_is_socmed==1 ~ "socmed")

socmed <-rename(socmed, data_channel = data_channel_is_socmed)


#Data channel is tech
tech <- filter(newsDataTrain,  data_channel_is_tech == 1) %>%
  select( data_channel_is_tech, shares,  n_tokens_content)

    tech$data_channel_is_tech <- case_when(
      tech$data_channel_is_tech==1 ~ "tech")

tech <-rename(tech, data_channel = data_channel_is_tech)


#Data channel is world
world <- filter(newsDataTrain,  data_channel_is_world == 1) %>%
  select( data_channel_is_world, shares,  n_tokens_content)

    world$data_channel_is_world <- case_when(
      world$data_channel_is_world==1 ~ "world")

world <-rename(world, data_channel = data_channel_is_world)


# Union Data
channels <- union(lifestyle, entertainment)
channels <- union(channels, bus)
channels <- union(channels, socmed)
channels <- union(channels, tech)
channels <- union(channels, world)
```

# _Graphs_

## Barchart
The below barchart shows the count for each data channel when it equals 1 or is active. As you can see, world, tech, and entertainment's frequency are very high while lifestyle and socmed are very low.

```{r plot1}
# Plots

ggplot(channels, aes(data_channel)) +
  geom_bar()
```

## Boxplot
Below displays boxplots for shares broken by data channel.We can see that there's outliers for the shares. All the data channels seem to have condensed measure of center, especially bus.This should make predicting shares easier for some data_channels.

```{r plot2}
ggplot(channels, aes(x = data_channel, y = shares))+ 
  geom_jitter(aes(color = data_channel)) + ggtitle("Boxplot for Shares") + 
  geom_boxplot() 
```

## Scatterplot
The scatterplots below represent the total words in the content vs shares broken down by each data_channel. We can see that all the data_channels try to the words below 2000 except for some outliers. This must be to maintain the attention of the readers as the shares are the highest in this area.

```{r plot3}
ggplot(channels, aes(x = n_tokens_content, y = shares, group = data_channel)) + geom_point(aes(color = data_channel)) + geom_smooth(method = 'lm', color = 'green') +
  ggtitle("Number of Words in Content vs Shares") + facet_wrap(~data_channel)

```


# _Modeling_
Goal: Create models for predicting the shares variable.

## Regression Tree  
A (not ensemble) tree-based model chosen using leave one out cross validation  
Root MSE is used on the test data set to see how well the model is.  
```{r regressiontree}

# a (not ensemble) tree-based model chosen using leave one out cross validation
# Regression Tree
treeFit <- tree(shares ~ . ,data = newsDataTrain)
plot(treeFit); text(treeFit)

cvTree <- cv.tree(treeFit); cvTree

# Visual of How CV Error Changes w/# of Nodes
plot(cvTree$size, cvTree$dev, type="b")

# Predictions usingpredict
pred <- predict(treeFit, newdata=dplyr::select(newsDataTest,-shares))

# Root MSE
sqrt(mean((pred-newsDataTest$shares)^2))

```


## Boosted Tree  
Model chosen using cross-validation  
Utilizing misclassification rate to evaluate the model.  
```{r boostedtree, warning=FALSE}

boostTree <- train(shares ~ ., data = newsDataTrain, method = "gbm",
trControl = trainControl(method = "repeatedcv", number = 4, repeats = 2),
preProcess = c("center", "scale"), verbose = FALSE)
boostTree

boostTbl <- table(data.frame(pred = predict(boostTree, newsDataTest), true = newsDataTest$shares))


#misclassificatoon rate to evaluate model
1-c(boost = sum(diag(boostTbl)/sum(boostTbl)))


```

## Linear Regression Model

The final model we will examine is a linear regression model. The model will be fit with all possible predictors using the `lm` function. Also, predictions utilizing this model will be made on the test set using `predict`. 

```{r, warning = FALSE}
lmfit <- lm(shares ~ ., data = newsDataTrain)
lmpred <- predict(lmfit, newdata = newsDataTest)
head(lmpred)        
```


```{r message = FALSE, results = "hide"}

render_html_fun <- function(hub_in){
  rmarkdown::render('Project-02.Rproj',
                    output_file = paste0('Project2', hub_in, "_", '.html'),
                    params = list(hub = hub_in, set_title = hub))}


hubs_input <- c("weekday_is_monday", "weekday_is_tuesday", "weekday_is_wednesday", 
                "weekday_is_thursday", "weekday_is_friday", "weekday_is_saturday", 
                "weekday_is_sunday")


walk(hubs_input, render_html_fun)

```


